---
title: "Photography"
description: |
  Life through a 35mm lens.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```
My grandfather once gifted me his old 35mm Olympus camera. I didn't know anything about taking photographs, plus I had my digital camera anyway (this was before smartphones). It was buried in a closet for years and I found it when I was moving to Marquette for college. I took a couple rolls of film with me and started practicing. It wasn't until I developed my first roll of film that I found the charm.  
  
* Each photo costs ~$1, is this moment worth capturing or simply enjoying?  
* The analog grain creates a softer, warmer feeling.  
* Sometimes the film gets damaged and creates a certain uniqueness.  
* You only get one shot. That's it.  
  
This hobby brings me back to the present. Observing the environment; waiting for the perfect moment. Here are some of my favorites I've taken over the years. Enjoy!
    
```{r}
#slickR::slickR(
#    list.files("photos/photography",full.names = TRUE),
#    height = 400,
#    width = '95%') +
#  slickR::settings(dots = T, autoplay = T)

```